---
title: "Introduction"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center")
  knitr::opts_knit$set(width=75)

# Swipe environment
  rm(list=ls())
  
# Load packages
  library(eeptools)
  library(dplyr)
  library(kableExtra)
  library(rmdformats)
  library(sjmisc)
  library(summarytools)
  library(stats)
  library(tidyverse)
  library(XLConnect)

# Round to 2 digits   
  options(digits=2)
  
```

# Overview of data sets 

```{r overview, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx", 
                               sheet = "all_data", 
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)
```


# Questionnaire data 

## Standardized questionnaires 

Transformations:

  + Recode value names
  + Calculate age based on birth date and test date
  + Calculate Winkler index
  + Calculate change scores 
  + Calculate composite scores
  + Calculate z-scores / mean-centered values for change scores / T1 / T2 / T3 / parental values for further analyses
  + !*Note*: For SDQ_Total, T1-T2 was calculated to invert the scale!
  + Calculate composite score of all behavioral variables
  
 <!-- Centering refers to: mean of values will be subtracted from all values, it does not change the scale:  scale(A, center = TRUE, scale = FALSE) -->
  
 <!-- zscore: changes the scale, one-unit difference = one SD difference : scale(A, center = TRUE, scale = TRUE) -->

```{r qn_data}

# Load questionnaire data
  qn_data = readWorksheetFromFile("./data/qn_data.xlsx",
                             sheet = 1,
                             startCol = 1,
                             endCol = 0)

# Re-code gender
  qn_data$sex[qn_data$sex == 1] = "Male"
  qn_data$sex[qn_data$sex == 2] = "Female"
  
# Re-code training group
  qn_data$group[qn_data$group == "ZE"] = "TG"
  qn_data$group[qn_data$group == "SB"] = "CG"

# Define N/A data
  qn_data[qn_data==-99] = NA
  
# Calculate age (Extract age from birth/test date)
  qn_data$age = as.numeric(cbind(age_calc(as.Date(qn_data$birth_date),
                                     as.Date(qn_data$test_date), units = "years"))) # Needs to be numeric to create table
  
# Remove birth and test date column
  qn_data = subset(qn_data, select=-c(birth_date,test_date))

# Calculate Winkler-Index 

  # Create Winkler Index 
  
    # For the Winkler Index, one awards points for income, occupation and education level of each
    # parent. Points range from 1-5. These points are added up. The maximum value would be 15 points.
    # For education and occupation, the parent with the larger score was chosen per family. 
  
  # Income
    # 1 = 0-1250 Euro
    # 2 = 1250-2000 Euro
    # 3 = 2000-3000 Euro,
    # 4 = 3000-5000 Euro
    # 5 = more than 5000 Euro
  
    qn_data$income_rec[qn_data$income==1 | qn_data$income==2 | qn_data$income==3 | qn_data$income==4] = 1
    qn_data$income_rec[qn_data$income==5 | qn_data$income==6 | qn_data$income==7] = 2
    qn_data$income_rec[qn_data$income==8 | qn_data$income==9 | qn_data$income==10] = 3
    qn_data$income_rec[qn_data$income==11 | qn_data$income==12] = 4
    qn_data$income_rec[qn_data$income==13] = 5
    
  # Education
    # 1 = no degree
    # 2 = secondary modern school [German: "Hauptschule"]
    # 3 = middle school [German: "Realschule"]
    # 4 = advanced technical college entrance qualification [German: "Fachhochschulreife"]
    # 5 = higher education entrance qualification (A-levels) [German: "Abitur"]
  
  # for mum
    qn_data$mum_ed_rec[qn_data$mum_ed==7 | qn_data$mum_ed==8] = 1
    qn_data$mum_ed_rec[qn_data$mum_ed==1 | qn_data$mum_ed==6] = 2
    qn_data$mum_ed_rec[qn_data$mum_ed==2 | qn_data$mum_ed==3] = 3
    qn_data$mum_ed_rec[qn_data$mum_ed==4] = 4
    qn_data$mum_ed_rec[qn_data$mum_ed==5] = 5

  
  # for dad
    qn_data$dad_ed_rec[qn_data$dad_ed==7 | qn_data$dad_ed==8] = 1
    qn_data$dad_ed_rec[qn_data$dad_ed==1 | qn_data$dad_ed==6] = 2
    qn_data$dad_ed_rec[qn_data$dad_ed==2 | qn_data$dad_ed==3] = 3
    qn_data$dad_ed_rec[qn_data$dad_ed==4] = 4
    qn_data$dad_ed_rec[qn_data$dad_ed==5] = 5
  
  # Occupation 
    # 1 = student
    # 2 = skilled worker [German:Gelernter "Facharbeiter"]
    # 3 = foremen/forwomen [German: "Vorarbeiter"]
    # 4 = clerk in the middle grade of the civil service [German: "Beamter mittlerer Dienst"]
    # 5 = senior officials [German: "Beamte höherer Dienst"]
  
  # for mum
    qn_data$occ_mum[qn_data$mum_occup_ISCO==5 | qn_data$mum_occup_ISCO==11 |
                      qn_data$mum_occup_ISCO==12 | qn_data$mum_occup_ISCO==51 | 
                      qn_data$mum_occup_ISCO==52] = 1
    
    qn_data$occ_mum[qn_data$mum_occup_ISCO==13 | qn_data$mum_occup_ISCO==21 |
                      qn_data$mum_occup_ISCO==26 | qn_data$mum_occup_ISCO==31 |
                      qn_data$mum_occup_ISCO==32] = 2
    
    qn_data$occ_mum[qn_data$mum_occup_ISCO==14 | qn_data$mum_occup_ISCO==33 | 
                      qn_data$mum_occup_ISCO==41] = 3
    
    qn_data$occ_mum[qn_data$mum_occup_ISCO==2 | qn_data$mum_occup_ISCO==22 | 
                      qn_data$mum_occup_ISCO==23 | qn_data$mum_occup_ISCO==24 |
                      qn_data$mum_occup_ISCO==34 | qn_data$mum_occup_ISCO==42] = 4
    
    qn_data$occ_mum[qn_data$mum_occup_ISCO==25 | 
                      qn_data$mum_occup_ISCO==35 | qn_data$mum_occup_ISCO==43 |
                      qn_data$mum_occup_ISCO==44] = 5
  
  # for dad
    qn_data$occ_dad[qn_data$dad_occup_ISCO==5 | qn_data$dad_occup_ISCO==11 |
                      qn_data$dad_occup_ISCO==12 | qn_data$dad_occup_ISCO==51 |
                      qn_data$dad_occup_ISCO==52] = 1
    
    qn_data$occ_dad[qn_data$dad_occup_ISCO==13 | qn_data$dad_occup_ISCO==21 | 
                      qn_data$dad_occup_ISCO==26 | qn_data$dad_occup_ISCO==31 | 
                      qn_data$dad_occup_ISCO==32] = 2
    
    qn_data$occ_dad[qn_data$dad_occup_ISCO==14 | qn_data$dad_occup_ISCO==33 | 
                      qn_data$dad_occup_ISCO==41] = 3
    
    qn_data$occ_dad[qn_data$dad_occup_ISCO==2 | qn_data$dad_occup_ISCO==22 | 
                      qn_data$dad_occup_ISCO==23 | qn_data$dad_occup_ISCO==24 |
                      qn_data$dad_occup_ISCO==34 | qn_data$dad_occup_ISCO==42] = 4
    
    qn_data$occ_dad[qn_data$dad_occup_ISCO==25 | qn_data$dad_occup_ISCO==35 |
                      qn_data$dad_occup_ISCO==43 | qn_data$dad_occup_ISCO==44] = 5
  
  # Calculate Winkler index
    # Sum up all points (choose the parent with the larger score). 
  
    for (h in 1:length(qn_data$ID)){
      qn_data$wink_ind[h] = sum(qn_data$income_rec[h],
                            max(qn_data$occ_dad[h],qn_data$occ_mum[h]),
                            max(qn_data$mum_ed_rec[h],qn_data$dad_ed_rec[h]))
    }
     
  
# Remove extra SES data columns
  qn_data = subset(qn_data, select=-c(mum_occup_ISCO,dad_occup_ISCO, income, mum_ed, dad_ed, occ_mum, occ_dad, income_rec, dad_ed_rec, mum_ed_rec))
  
# Choose data
  qn_data = subset(qn_data, EEG_PFV == 1)
  qn_data = subset(qn_data, Exclude == 0) 
  qn_data = subset (qn_data, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)  
  
# Z-scoring for T1/T2/T3/parental values
  qn_data$z_GEM_T1 = scale(qn_data$GEM_Total_T1)
  qn_data$z_GEM_T2 = scale(qn_data$GEM_Total_T2)
  qn_data$z_GEM_T3 = scale(qn_data$GEM_Total_T3)
  qn_data$z_EMK_EM_P_T1 = scale(qn_data$EMK_EM_P_T1)
  qn_data$z_EMK_EM_P_T2 = scale(qn_data$EMK_EM_P_T2)
  qn_data$z_EMK_EM_P_T3 = scale(qn_data$EMK_EM_P_T3)
  qn_data$z_EMK_EM_CH_T1 = scale(qn_data$EMK_EM_CH_T1)
  qn_data$z_EMK_EM_CH_T2 = scale(qn_data$EMK_EM_CH_T2)
  qn_data$z_EMK_EK_P_T1 = scale(qn_data$EMK_EK_P_T1)
  qn_data$z_EMK_EK_P_T2 = scale(qn_data$EMK_EK_P_T2)
  qn_data$z_EMK_EK_P_T3 = scale(qn_data$EMK_EK_P_T3)
  qn_data$z_EMK_EK_CH_T1 = scale(qn_data$EMK_EK_CH_T1)
  qn_data$z_EMK_EK_CH_T2 = scale(qn_data$EMK_EK_CH_T2)
  qn_data$z_EMK_PB_CH_T1 = scale(qn_data$EMK_PB_CH_T1)
  qn_data$z_EMK_PB_CH_T2 = scale(qn_data$EMK_PB_CH_T2)
  qn_data$z_SDQ_PB_T1 = scale(qn_data$SDQ_PB_T1)
  qn_data$z_SDQ_PB_T2 = scale(qn_data$SDQ_PB_T2)
  qn_data$z_SDQ_PB_T3 = scale(qn_data$SDQ_PB_T3)
  qn_data$z_SDQ_T1 = scale(qn_data$SDQ_Total_T1)
  qn_data$z_SDQ_T2= scale(qn_data$SDQ_Total_T2)  
  qn_data$z_SDQ_T3= scale(qn_data$SDQ_Total_T3)  
  qn_data$z_SEFQ_Pos_Exp = scale(qn_data$SEFQ_Pos_Exp)
  qn_data$z_SEFQ_Neg_Exp = scale(qn_data$SEFQ_Neg_Exp)
  qn_data$z_wink_ind = scale(qn_data$wink_ind)
  qn_data$z_SPF_Pers_tak = scale(qn_data$SPF_Pers_tak)
  qn_data$z_SPF_Emp_conc= scale(qn_data$SPF_Emp_conc)

# Mean-centering for T1/T2/T3/parental values
  qn_data$mc_GEM_T1 = scale(qn_data$GEM_Total_T1, scale = F)
  qn_data$mc_GEM_T2 = scale(qn_data$GEM_Total_T2, scale = F)
  qn_data$mc_GEM_T3 = scale(qn_data$GEM_Total_T3, scale = F)
  qn_data$mc_EMK_EM_P_T1 = scale(qn_data$EMK_EM_P_T1, scale = F)
  qn_data$mc_EMK_EM_P_T2 = scale(qn_data$EMK_EM_P_T2, scale = F)
  qn_data$mc_EMK_EM_P_T3 = scale(qn_data$EMK_EM_P_T3, scale = F)
  qn_data$mc_EMK_EM_CH_T1 = scale(qn_data$EMK_EM_CH_T1, scale = F)
  qn_data$mc_EMK_EM_CH_T2 = scale(qn_data$EMK_EM_CH_T2, scale = F)
  qn_data$mc_EMK_EK_P_T1 = scale(qn_data$EMK_EK_P_T1, scale = F)
  qn_data$mc_EMK_EK_P_T2 = scale(qn_data$EMK_EK_P_T2, scale = F)
  qn_data$mc_EMK_EK_P_T3 = scale(qn_data$EMK_EK_P_T3, scale = F)
  qn_data$mc_EMK_EK_CH_T1 = scale(qn_data$EMK_EK_CH_T1, scale = F)
  qn_data$mc_EMK_EK_CH_T2 = scale(qn_data$EMK_EK_CH_T2, scale = F)
  qn_data$mc_EMK_PB_CH_T1 = scale(qn_data$EMK_PB_CH_T1, scale = F)
  qn_data$mc_EMK_PB_CH_T2 = scale(qn_data$EMK_PB_CH_T2, scale = F)
  qn_data$mc_SDQ_PB_T1 = scale(qn_data$SDQ_PB_T1, scale = F)
  qn_data$mc_SDQ_PB_T2 = scale(qn_data$SDQ_PB_T2, scale = F)
  qn_data$mc_SDQ_PB_T3 = scale(qn_data$SDQ_PB_T3, scale = F)
  qn_data$mc_SDQ_T1 = scale(qn_data$SDQ_Total_T1, scale = F)
  qn_data$mc_SDQ_T2= scale(qn_data$SDQ_Total_T2, scale = F)  
  qn_data$mc_SDQ_T3= scale(qn_data$SDQ_Total_T3, scale = F)  
  qn_data$mc_SEFQ_Pos_Exp = scale(qn_data$SEFQ_Pos_Exp, scale = F)
  qn_data$mc_SEFQ_Neg_Exp = scale(qn_data$SEFQ_Neg_Exp, scale = F)
  qn_data$mc_wink_ind = scale(qn_data$wink_ind, scale = F)
  qn_data$mc_SPF_Pers_tak = scale(qn_data$SPF_Pers_tak, scale = F)
  qn_data$mc_SPF_Emp_conc= scale(qn_data$SPF_Emp_conc, scale = F)  
  
# Calculate change scores (d = delta) for T2
  qn_data$d_GEM_CE = qn_data$GEM_CE_T2 - qn_data$GEM_CE_T1
  qn_data$d_GEM_AE = qn_data$GEM_AE_T2 - qn_data$GEM_AE_T1
  qn_data$d_GEM_Total = qn_data$GEM_Total_T2 - qn_data$GEM_Total_T1
  qn_data$d_EMK_EM_CH = qn_data$EMK_EM_CH_T2 - qn_data$EMK_EM_CH_T1
  qn_data$d_EMK_EM_P = qn_data$EMK_EM_P_T2 - qn_data$EMK_EM_P_T1
  qn_data$d_EMK_EK_CH = qn_data$EMK_EK_CH_T2 - qn_data$EMK_EK_CH_T1
  qn_data$d_EMK_EK_P = qn_data$EMK_EK_P_T2 - qn_data$EMK_EK_P_T1
  qn_data$d_EMK_PB_CH = qn_data$EMK_PB_CH_T2 - qn_data$EMK_PB_CH_T1
  qn_data$d_SDQ_PB = qn_data$SDQ_PB_T2 - qn_data$SDQ_PB_T1
  qn_data$d_SDQ_EP = qn_data$SDQ_EP_T2 - qn_data$SDQ_EP_T1
  qn_data$d_SDQ_Total = qn_data$SDQ_Total_T1 - qn_data$SDQ_Total_T2
  qn_data$d_SRS = qn_data$SRS_T2 - qn_data$SRS_T1
  
# Calculate z-scores of change scores (d = delta) for T2
  qn_data$zd_GEM_CE = scale(qn_data$d_GEM_CE)
  qn_data$zd_GEM_AE = scale(qn_data$d_GEM_AE)
  qn_data$zd_GEM_Total = scale(qn_data$d_GEM_Total) 
  qn_data$zd_EMK_EM_CH = scale(qn_data$d_EMK_EM_CH)
  qn_data$zd_EMK_EM_P = scale(qn_data$d_EMK_EM_P)
  qn_data$zd_EMK_EK_CH = scale(qn_data$d_EMK_EK_CH)
  qn_data$zd_EMK_EK_P = scale(qn_data$d_EMK_EK_P)
  qn_data$zd_EMK_PB_CH = scale(qn_data$d_EMK_PB_CH)
  qn_data$zd_SDQ_PB = scale(qn_data$d_SDQ_PB)
  qn_data$zd_SDQ_EP = scale(qn_data$d_SDQ_EP)
  qn_data$zd_SDQ_Total = scale(qn_data$d_SDQ_Total)
  qn_data$zd_SRS = scale(qn_data$d_SRS)
  
# Calculate mean-centered change scores (d = delta) for T2
  qn_data$mcd_GEM_CE = scale(qn_data$d_GEM_CE, scale = F)
  qn_data$mcd_GEM_AE = scale(qn_data$d_GEM_AE, scale = F)
  qn_data$mcd_GEM_Total = scale(qn_data$d_GEM_Total, scale = F) 
  qn_data$mcd_EMK_EM_CH = scale(qn_data$d_EMK_EM_CH, scale = F)
  qn_data$mcd_EMK_EM_P = scale(qn_data$d_EMK_EM_P, scale = F)
  qn_data$mcd_EMK_EK_CH = scale(qn_data$d_EMK_EK_CH, scale = F)
  qn_data$mcd_EMK_EK_P = scale(qn_data$d_EMK_EK_P, scale = F)
  qn_data$mcd_EMK_PB_CH = scale(qn_data$d_EMK_PB_CH, scale = F)
  qn_data$mcd_SDQ_PB = scale(qn_data$d_SDQ_PB, scale = F)
  qn_data$mcd_SDQ_EP = scale(qn_data$d_SDQ_EP, scale = F)
  qn_data$mcd_SDQ_Total = scale(qn_data$d_SDQ_Total, scale = F)
  qn_data$mcd_SRS = scale(qn_data$d_SRS, scale = F)
  
# Calculate EMK composite scores (empathy (parent / child) and emotion knowledge (parent/child)) using z-scores
  qn_data$zd_EMK_EM_comp = scale(qn_data$d_EMK_EM_CH) + scale(qn_data$d_EMK_EM_P)
  qn_data$zd_EMK_EK_comp = scale(qn_data$d_EMK_EK_CH) + scale(qn_data$d_EMK_EK_P)
  
# Calculate change scores (d = delta) for T3
  qn_data$d_GEM_Total_lt = qn_data$GEM_Total_T3 - qn_data$GEM_Total_T2
  qn_data$d_EMK_EM_P_lt = qn_data$EMK_EM_P_T3 - qn_data$EMK_EM_P_T2
  qn_data$d_EMK_EK_P_lt = qn_data$EMK_EK_P_T3 - qn_data$EMK_EK_P_T2
  qn_data$d_SDQ_PB_lt = qn_data$SDQ_PB_T3 - qn_data$SDQ_PB_T2
  qn_data$d_SDQ_Total_lt = qn_data$SDQ_Total_T2 - qn_data$SDQ_Total_T3
  
# Calculate z-scores of change scores (d = delta) for T3
  qn_data$zd_GEM_Total_lt = scale(qn_data$d_GEM_Total_lt) 
  qn_data$zd_EMK_EM_P_lt = scale(qn_data$d_EMK_EM_P_lt)
  qn_data$zd_EMK_EK_P_lt = scale(qn_data$d_EMK_EK_P_lt)
  qn_data$zd_SDQ_PB_lt = scale(qn_data$d_SDQ_PB_lt)
  qn_data$zd_SDQ_Total_lt = scale(qn_data$d_SDQ_Total_lt)
    
# Calculate mean-centered change scores (d = delta) for T3
  qn_data$mcd_GEM_Total_lt = scale(qn_data$d_GEM_Total_lt, scale = F) 
  qn_data$mcd_EMK_EM_P_lt = scale(qn_data$d_EMK_EM_P_lt, scale = F)
  qn_data$mcd_EMK_EK_P_lt = scale(qn_data$d_EMK_EK_P_lt, scale = F)
  qn_data$mcd_SDQ_PB_lt = scale(qn_data$d_SDQ_PB_lt, scale = F)
  qn_data$mcd_SDQ_Total_lt = scale(qn_data$d_SDQ_Total_lt, scale = F)
  
# Z-scoring for covariates 
  qn_data$z_age = scale(qn_data$age)
  qn_data$z_CPM = scale(qn_data$CPM)
  qn_data$z_app_time = scale(qn_data$T_Self_Report) 
  
# Mean-centering for covariates 
  qn_data$mc_age = scale(qn_data$age, scale = F)
  qn_data$mc_CPM = scale(qn_data$CPM, scale = F)
  qn_data$mc_app_time = scale(qn_data$T_Self_Report, scale = F)   
  
# Calculate composite score
  qn_data$comp = qn_data$zd_GEM_Total + qn_data$zd_EMK_EK_CH + qn_data$zd_EMK_EK_P + qn_data$zd_EMK_EM_P +
                 qn_data$zd_EMK_EM_CH + qn_data$zd_EMK_PB_CH + qn_data$zd_SDQ_PB + qn_data$zd_SDQ_Total  

```

## App-based questionnaire

```{r app_qn}

# Load questionnaire data
  app_qn = readWorksheetFromFile("./data/app_qn.xlsx",
                             sheet = 1,
                             startCol = 1,
                             endCol = 0)

# Define N/A data
  app_qn[app_qn==-99] = NA

# Choose data
  # Choose data
  app_qn = subset (app_qn, ID != 1 & ID != 11 & ID != 21 & ID != 30 & ID != 36 & ID != 48 &  ID != 54 & ID != 58 & ID != 70 & ID != 75) 
  app_qn = subset(app_qn, EEG_PFV == 1)
  app_qn = subset(app_qn, Exclude == 0)  

# Define N/A data
  app_qn[app_qn==99] = NA
  
# Re-code group
  app_qn$App[app_qn$App == 1] = "TG"
  app_qn$App[app_qn$App == 2] = "CG"
  
  
# Save in Rdata format
  save(app_qn, file = "./data/app_qn.RData")  


# Get info for module 4
  qn_data$mod_4 = app_qn$mod_4
  
```

# ERP data

## ERP visualization data

  + Re-name conditions
  
```{r ERP_vis_data}

# Averaged P1/P3 trajectories per participant 
  P1_P3_traj = read.delim("./data/P1_P3_traj.txt", header = TRUE, sep = " ", dec = ".")
  
# Averaged N170 left / N170 right trajectories per participant 
  N170_l_traj = read.delim("./data/N170_l_traj.txt", header = TRUE, sep = " ", dec = ".")
  N170_r_traj = read.delim("./data/N170_r_traj.txt", header = TRUE, sep = " ", dec = ".")

# Add info which ROI is included    
  P1_P3_traj$ERP = 'P1_P3'
  N170_l_traj$ERP = 'N170l'
  N170_r_traj$ERP = 'N170r'
  
# Combine data sets
  erp_vis_data = rbind(P1_P3_traj, N170_l_traj, N170_r_traj)
  
# De-select ape faces (event code: 4)
  erp_vis_data = subset(erp_vis_data, cond != 4)  
  
# Rename condition
  erp_vis_data$cond[erp_vis_data$cond == 1]='happy'
  erp_vis_data$cond[erp_vis_data$cond == 2]='neutral'
  erp_vis_data$cond[erp_vis_data$cond == 3]='angry'

# Calculate median split for age
  qn_data$age_split = dicho(as.numeric(qn_data$age), dich.by = "median")
  
# Rename age_split variable
  qn_data$age_split = as.numeric(qn_data$age_split)
  qn_data$age_split[qn_data$age_split == 1]='young'
  qn_data$age_split[qn_data$age_split == 2]='old'
 
# Match info of qn_data with EEG data
  erp_vis_data$group = qn_data$group[match(erp_vis_data$ID, qn_data$ID,nomatch = NA)]
  erp_vis_data$group = factor(erp_vis_data$group) 
  erp_vis_data$age_split = qn_data$age_split[match(erp_vis_data$ID, qn_data$ID,nomatch = NA)]
  erp_vis_data$age_split = factor(erp_vis_data$age_split)  
  erp_vis_data$sex = qn_data$sex[match(erp_vis_data$ID, qn_data$ID,nomatch = NA)]
  erp_vis_data$sex = factor(erp_vis_data$sex)
  erp_vis_data$exc = qn_data$Exclude[match(erp_vis_data$ID, qn_data$ID,nomatch = NA)]
  
# De-select participants  
  erp_vis_data = subset(erp_vis_data, exc == 0)
  erp_vis_data = subset (erp_vis_data, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)

# Save in Rdata format
  save(erp_vis_data, file = "./data/erp_vis_data.RData")  

```

## ERP statistical data

  + Re-name conditions
  + Match ERP and behavioral data 
  + Average ERPs for each participant
  + Get trial count per condition / per participant
  + Calculate z-scores

```{r ERP_stat_data} 

## P1

# Get P1 data
  P1 = read.delim("./data/P1_singl_trial_data.txt", header = TRUE, sep = " ", dec = ".") 

# Load questionnaire data
  stim = readWorksheetFromFile("./data/stim_info.xlsx", 
                             sheet = 1, 
                             startCol = 1,
                             endCol = 0) 
  
# Match questionnaire data
  P1$age = qn_data$age[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$z_age = qn_data$z_age[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$group = qn_data$group[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$sex = qn_data$sex[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$app_time = qn_data$T_Self_Report[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$z_app_time = qn_data$z_app_time[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$app_eng = qn_data$app_compl[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$CPM = qn_data$CPM[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$z_CPM = qn_data$z_CPM[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_GEM_CE = qn_data$d_GEM_CE[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_GEM_AE = qn_data$d_GEM_AE[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_GEM_Total = qn_data$d_GEM_Total[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_EMK_EM_CH = qn_data$d_EMK_EM_CH[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_EMK_EM_P = qn_data$d_EMK_EM_P[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_EMK_EK_CH = qn_data$d_EMK_EK_CH[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_EMK_EK_P = qn_data$d_EMK_EK_P[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_EMK_PB_CH = qn_data$d_EMK_PB_CH[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_SDQ_PB = qn_data$d_SDQ_PB[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_SDQ_EP = qn_data$d_SDQ_EP[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_SDQ_Total = qn_data$d_SDQ_Total[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$d_SRS = qn_data$d_SRS[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$GEM_CE_T1 = qn_data$GEM_CE_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$GEM_AE_T1 = qn_data$GEM_AE_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$GEM_Total_T1 = qn_data$GEM_Total_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$EMK_EM_CH_T1 = qn_data$EMK_EM_CH_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$EMK_EM_P_T1 = qn_data$EMK_EM_P_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$EMK_EK_CH_T1 = qn_data$EMK_EK_CH_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$EMK_EK_P_T1 = qn_data$EMK_EK_P_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$EMK_PB_CH_T1 = qn_data$EMK_PB_CH_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$SDQ_PB_T1 = qn_data$SDQ_PB_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$SDQ_EP_T1 = qn_data$SDQ_EP_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$SDQ_Total_T1 = qn_data$SDQ_Total_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$SRS_T1 = qn_data$SRS_T1[match(P1$ID, qn_data$ID,nomatch = NA)]
  P1$exc = qn_data$Exclude[match(P1$ID, qn_data$ID,nomatch = NA)]
  
# Match stimulus info
  P1$stim_ID = stim$Stim_ID[match(P1$Trial, stim$Position, nomatch = NA)]  
  P1$stim_emo = stim$Stim_Emotion[match(P1$Trial, stim$Position, nomatch = NA)]  
  P1$stim_sex = stim$Stim_Sex[match(P1$Trial, stim$Position, nomatch = NA)]  
  P1$block = stim$Block[match(P1$Trial, stim$Position, nomatch = NA)]  
  
# Re-order data frame
  P1 = subset(P1, select=c(ID, group, age, z_age, sex, emotion,
                           exc, ROI_GA_amp, ROI_GA_lat, Trial, block,
                           stim_ID, stim_emo, stim_sex, app_time:SRS_T1, PO3_amp:PO10_lat))

# De-select ape faces and AD trials  
  P1_stat = subset(P1, emotion != 4)
  
# De-select participants  
  P1_stat = subset(P1_stat, exc == 0)  
  
# Rename emotion
  P1_stat$emotion[P1_stat$emotion == 1]='happy'
  P1_stat$emotion[P1_stat$emotion == 2]='neutral'
  P1_stat$emotion[P1_stat$emotion == 3]='angry'  

##### N170
  
# Get N170 data
  N170l = read.delim("./data/N170_l_singl_trial_data.txt", header = TRUE, sep = " ", dec = ".") 
  N170r = read.delim("./data/N170_r_singl_trial_data.txt", header = TRUE, sep = " ", dec = ".") 

# Combine N170 left and right hemisphere 
  N170l = N170l[,-c(1:3, 5:7)]
  N170r = N170r[,-c(1:3, 5:7)]
  N170 = rbind(N170l, N170r)
  
# Match questionnaire data
  N170$age = qn_data$age[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$z_age = qn_data$z_age[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$group = qn_data$group[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$sex = qn_data$sex[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$app_time = qn_data$T_Self_Report[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$z_app_time = qn_data$z_app_time[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$app_eng = qn_data$app_compl[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$CPM = qn_data$CPM[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$z_CPM = qn_data$z_CPM[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_GEM_CE = qn_data$d_GEM_CE[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_GEM_AE = qn_data$d_GEM_AE[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_GEM_Total = qn_data$d_GEM_Total[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_EMK_EM_CH = qn_data$d_EMK_EM_CH[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_EMK_EM_P = qn_data$d_EMK_EM_P[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_EMK_EK_CH = qn_data$d_EMK_EK_CH[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_EMK_EK_P = qn_data$d_EMK_EK_P[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_EMK_PB_CH = qn_data$d_EMK_PB_CH[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_SDQ_PB = qn_data$d_SDQ_PB[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_SDQ_EP = qn_data$d_SDQ_EP[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_SDQ_Total = qn_data$d_SDQ_Total[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$d_SRS = qn_data$d_SRS[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$GEM_CE_T1 = qn_data$GEM_CE_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$GEM_AE_T1 = qn_data$GEM_AE_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$GEM_Total_T1 = qn_data$GEM_Total_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$EMK_EM_CH_T1 = qn_data$EMK_EM_CH_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$EMK_EM_P_T1 = qn_data$EMK_EM_P_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$EMK_EK_CH_T1 = qn_data$EMK_EK_CH_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$EMK_EK_P_T1 = qn_data$EMK_EK_P_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$EMK_PB_CH_T1 = qn_data$EMK_PB_CH_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$SDQ_PB_T1 = qn_data$SDQ_PB_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$SDQ_EP_T1 = qn_data$SDQ_EP_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$SDQ_Total_T1 = qn_data$SDQ_Total_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$SRS_T1 = qn_data$SRS_T1[match(N170$ID, qn_data$ID,nomatch = NA)]
  N170$exc = qn_data$Exclude[match(N170$ID, qn_data$ID,nomatch = NA)]

# Match stimulus info
  N170$stim_ID = stim$Stim_ID[match(N170$Trial, stim$Position, nomatch = NA)]  
  N170$stim_emo = stim$Stim_Emotion[match(N170$Trial, stim$Position, nomatch = NA)]  
  N170$stim_sex = stim$Stim_Sex[match(N170$Trial, stim$Position, nomatch = NA)]  
  N170$block = stim$Block[match(N170$Trial, stim$Position, nomatch = NA)]    
  
# Re-order data frame
  N170 = subset(N170, select=c(ID, group, age, z_age, sex, emotion, exc, ROI_GA_amp, ROI_GA_lat, hem, Trial, block, stim_ID, stim_emo, stim_sex, app_time:SRS_T1))
  
# De-select ape faces and AD trials  
  N170_stat = subset(N170, emotion != 4)
  
# De-select participants  
  N170_stat = subset(N170_stat, exc == 0)    
  
# Rename emotion
  N170_stat$emotion[N170_stat$emotion == 1]='happy'
  N170_stat$emotion[N170_stat$emotion == 2]='neutral'
  N170_stat$emotion[N170_stat$emotion == 3]='angry'  
  
# Rename hemisphere
  N170_stat$hem[N170_stat$hem == 1]='left'
  N170_stat$hem[N170_stat$hem == 2]='right' 
  
# De-select participants  
  P1_stat = subset (P1_stat, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75) 
  N170_stat = subset (N170_stat,ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)

# Save in Rdata format
  save(P1_stat, file = "./data/P1_stat.RData")  
  save(N170_stat, file = "./data/N170_stat.RData")  
  
```

```{r P3_stat_data}

##### P3
  
# Get P3 data
  P3_short = read.delim("./data/P3_singl_trial_data_short.txt", header = TRUE, sep = " ", dec = ".") 
  
# Match questionnaire data
  P3_short$age = qn_data$age[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$z_age = qn_data$z_age[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$group = qn_data$group[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$sex = qn_data$sex[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$app_time = qn_data$T_Self_Report[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$z_app_time = qn_data$z_app_time[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$app_eng = qn_data$app_compl[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$CPM = qn_data$CPM[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$z_CPM = qn_data$z_CPM[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_GEM_CE = qn_data$d_GEM_CE[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_GEM_AE = qn_data$d_GEM_AE[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_GEM_Total = qn_data$d_GEM_Total[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_EMK_EM_CH = qn_data$d_EMK_EM_CH[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_EMK_EM_P = qn_data$d_EMK_EM_P[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_EMK_EK_CH = qn_data$d_EMK_EK_CH[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_EMK_EK_P = qn_data$d_EMK_EK_P[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_EMK_PB_CH = qn_data$d_EMK_PB_CH[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_SDQ_PB = qn_data$d_SDQ_PB[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_SDQ_EP = qn_data$d_SDQ_EP[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_SDQ_Total = qn_data$d_SDQ_Total[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$d_SRS = qn_data$d_SRS[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$GEM_CE_T1 = qn_data$GEM_CE_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$GEM_AE_T1 = qn_data$GEM_AE_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$GEM_Total_T1 = qn_data$GEM_Total_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$EMK_EM_CH_T1 = qn_data$EMK_EM_CH_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$EMK_EM_P_T1 = qn_data$EMK_EM_P_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$EMK_EK_CH_T1 = qn_data$EMK_EK_CH_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$EMK_EK_P_T1 = qn_data$EMK_EK_P_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$EMK_PB_CH_T1 = qn_data$EMK_PB_CH_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$SDQ_PB_T1 = qn_data$SDQ_PB_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$SDQ_EP_T1 = qn_data$SDQ_EP_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$SDQ_Total_T1 = qn_data$SDQ_Total_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$SRS_T1 = qn_data$SRS_T1[match(P3_short$ID, qn_data$ID,nomatch = NA)]
  P3_short$exc = qn_data$Exclude[match(P3_short$ID, qn_data$ID,nomatch = NA)]

  
# Match stimulus info
  P3_short$stim_ID = stim$Stim_ID[match(P3_short$Trial, stim$Position, nomatch = NA)]  
  P3_short$stim_emo = stim$Stim_Emotion[match(P3_short$Trial, stim$Position, nomatch = NA)]  
  P3_short$stim_sex = stim$Stim_Sex[match(P3_short$Trial, stim$Position, nomatch = NA)]  
  P3_short$block = stim$Block[match(P3_short$Trial, stim$Position, nomatch = NA)]  
  
# Re-order data frame
  P3_short = subset(P3_short, select=c(ID, group, age, z_age, sex, emotion, exc, ROI_GA_amp, Trial, block, stim_ID, stim_emo, stim_sex, app_time:SRS_T1,PO3_amp:PO10_amp))

# De-select ape faces and AD trials  
  P3_short_stat = subset(P3_short, emotion != 4)
  
# De-select participants  
  P3_short_stat = subset(P3_short_stat, exc == 0)     
  
# Rename emotion
  P3_short_stat$emotion[P3_short_stat$emotion == 1]='happy'
  P3_short_stat$emotion[P3_short_stat$emotion == 2]='neutral'
  P3_short_stat$emotion[P3_short_stat$emotion == 3]='angry'  

# De-select participants  
  P3_short_stat = subset (P3_short_stat, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)

# Save in Rdata format
  save(P3_short_stat, file = "./data/P3_short_stat.RData")  
  
  
#########  
  
# Get P3 data
  P3_medium = read.delim("./data/P3_singl_trial_data_medium.txt", header = TRUE, sep = " ", dec = ".") 
  
# Match questionnaire data
  P3_medium$age = qn_data$age[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$z_age = qn_data$z_age[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$group = qn_data$group[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$sex = qn_data$sex[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$app_time = qn_data$T_Self_Report[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$z_app_time = qn_data$z_app_time[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$app_eng = qn_data$app_compl[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$CPM = qn_data$CPM[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$z_CPM = qn_data$z_CPM[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_GEM_CE = qn_data$d_GEM_CE[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_GEM_AE = qn_data$d_GEM_AE[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_GEM_Total = qn_data$d_GEM_Total[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_EMK_EM_CH = qn_data$d_EMK_EM_CH[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_EMK_EM_P = qn_data$d_EMK_EM_P[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_EMK_EK_CH = qn_data$d_EMK_EK_CH[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_EMK_EK_P = qn_data$d_EMK_EK_P[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_EMK_PB_CH = qn_data$d_EMK_PB_CH[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_SDQ_PB = qn_data$d_SDQ_PB[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_SDQ_EP = qn_data$d_SDQ_EP[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_SDQ_Total = qn_data$d_SDQ_Total[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$d_SRS = qn_data$d_SRS[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$GEM_CE_T1 = qn_data$GEM_CE_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$GEM_AE_T1 = qn_data$GEM_AE_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$GEM_Total_T1 = qn_data$GEM_Total_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$EMK_EM_CH_T1 = qn_data$EMK_EM_CH_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$EMK_EM_P_T1 = qn_data$EMK_EM_P_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$EMK_EK_CH_T1 = qn_data$EMK_EK_CH_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$EMK_EK_P_T1 = qn_data$EMK_EK_P_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$EMK_PB_CH_T1 = qn_data$EMK_PB_CH_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$SDQ_PB_T1 = qn_data$SDQ_PB_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$SDQ_EP_T1 = qn_data$SDQ_EP_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$SDQ_Total_T1 = qn_data$SDQ_Total_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$SRS_T1 = qn_data$SRS_T1[match(P3_medium$ID, qn_data$ID,nomatch = NA)]
  P3_medium$exc = qn_data$Exclude[match(P3_medium$ID, qn_data$ID,nomatch = NA)]

  
# Match stimulus info
  P3_medium$stim_ID = stim$Stim_ID[match(P3_medium$Trial, stim$Position, nomatch = NA)]  
  P3_medium$stim_emo = stim$Stim_Emotion[match(P3_medium$Trial, stim$Position, nomatch = NA)]  
  P3_medium$stim_sex = stim$Stim_Sex[match(P3_medium$Trial, stim$Position, nomatch = NA)]  
  P3_medium$block = stim$Block[match(P3_medium$Trial, stim$Position, nomatch = NA)]  
  
# Re-order data frame
  P3_medium = subset(P3_medium, select=c(ID, group, age, z_age, sex, emotion, exc, ROI_GA_amp, Trial, block, stim_ID, stim_emo, stim_sex, app_time:SRS_T1,PO3_amp:PO10_amp))

# De-select ape faces and AD trials  
  P3_medium_stat = subset(P3_medium, emotion != 4)
  
# De-select participants  
  P3_medium_stat = subset(P3_medium_stat, exc == 0)     
  
# Rename emotion
  P3_medium_stat$emotion[P3_medium_stat$emotion == 1]='happy'
  P3_medium_stat$emotion[P3_medium_stat$emotion == 2]='neutral'
  P3_medium_stat$emotion[P3_medium_stat$emotion == 3]='angry'  

# De-select participants  
  P3_medium_stat = subset (P3_medium_stat, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)

# Save in Rdata format
  save(P3_medium_stat, file = "./data/P3_medium_stat.RData")    
  
#########  
  
# Get P3 data
  P3_long = read.delim("./data/P3_singl_trial_data_long.txt", header = TRUE, sep = " ", dec = ".") 
  
# Match questionnaire data
  P3_long$age = qn_data$age[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$z_age = qn_data$z_age[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$group = qn_data$group[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$sex = qn_data$sex[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$app_time = qn_data$T_Self_Report[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$z_app_time = qn_data$z_app_time[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$app_eng = qn_data$app_compl[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$CPM = qn_data$CPM[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$z_CPM = qn_data$z_CPM[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_GEM_CE = qn_data$d_GEM_CE[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_GEM_AE = qn_data$d_GEM_AE[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_GEM_Total = qn_data$d_GEM_Total[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_EMK_EM_CH = qn_data$d_EMK_EM_CH[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_EMK_EM_P = qn_data$d_EMK_EM_P[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_EMK_EK_CH = qn_data$d_EMK_EK_CH[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_EMK_EK_P = qn_data$d_EMK_EK_P[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_EMK_PB_CH = qn_data$d_EMK_PB_CH[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_SDQ_PB = qn_data$d_SDQ_PB[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_SDQ_EP = qn_data$d_SDQ_EP[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_SDQ_Total = qn_data$d_SDQ_Total[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$d_SRS = qn_data$d_SRS[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$GEM_CE_T1 = qn_data$GEM_CE_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$GEM_AE_T1 = qn_data$GEM_AE_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$GEM_Total_T1 = qn_data$GEM_Total_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$EMK_EM_CH_T1 = qn_data$EMK_EM_CH_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$EMK_EM_P_T1 = qn_data$EMK_EM_P_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$EMK_EK_CH_T1 = qn_data$EMK_EK_CH_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$EMK_EK_P_T1 = qn_data$EMK_EK_P_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$EMK_PB_CH_T1 = qn_data$EMK_PB_CH_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$SDQ_PB_T1 = qn_data$SDQ_PB_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$SDQ_EP_T1 = qn_data$SDQ_EP_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$SDQ_Total_T1 = qn_data$SDQ_Total_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$SRS_T1 = qn_data$SRS_T1[match(P3_long$ID, qn_data$ID,nomatch = NA)]
  P3_long$exc = qn_data$Exclude[match(P3_long$ID, qn_data$ID,nomatch = NA)]

  
# Match stimulus info
  P3_long$stim_ID = stim$Stim_ID[match(P3_long$Trial, stim$Position, nomatch = NA)]  
  P3_long$stim_emo = stim$Stim_Emotion[match(P3_long$Trial, stim$Position, nomatch = NA)]  
  P3_long$stim_sex = stim$Stim_Sex[match(P3_long$Trial, stim$Position, nomatch = NA)]  
  P3_long$block = stim$Block[match(P3_long$Trial, stim$Position, nomatch = NA)]  
  
# Re-order data frame
  P3_long = subset(P3_long, select=c(ID, group, age, z_age,
                                     sex, emotion, exc, ROI_GA_amp, Trial, block, stim_ID, stim_emo, stim_sex,
                                     app_time:SRS_T1,PO3_amp:PO10_amp))

# De-select ape faces and AD trials  
  P3_long_stat = subset(P3_long, emotion != 4)
  
# De-select participants  
  P3_long_stat = subset(P3_long_stat, exc == 0)     
  
# Rename emotion
  P3_long_stat$emotion[P3_long_stat$emotion == 1]='happy'
  P3_long_stat$emotion[P3_long_stat$emotion == 2]='neutral'
  P3_long_stat$emotion[P3_long_stat$emotion == 3]='angry'  

# De-select participants  
  P3_long_stat = subset (P3_long_stat, ID != 1 & ID != 30 & ID != 36 & ID != 54 & ID != 58 & ID != 70 & ID != 75)

# Save in Rdata format
  save(P3_long_stat, file = "./data/P3_long_stat.RData")      

```

```{r calc_ERP_av_trial_num}

# Calculate amplitude mean for each ERP component and difference scores between emotions 

# P1
  P1_mean_amp = aggregate(P1_stat$ROI_GA_amp,
            list(ID = P1_stat$ID,
            emotion = P1_stat$emotion), mean)

  qn_data$P1_amp_hap = P1_mean_amp[P1_mean_amp$emotion == 'happy',]$x
  qn_data$P1_amp_ang = P1_mean_amp[P1_mean_amp$emotion == 'angry',]$x
  qn_data$P1_amp_neu = P1_mean_amp[P1_mean_amp$emotion == 'neutral',]$x
  
  qn_data$P1_amp_hap_neu = P1_mean_amp[P1_mean_amp$emotion == 'happy',]$x - P1_mean_amp[P1_mean_amp$emotion == 'neutral',]$x
  qn_data$P1_amp_ang_neu = P1_mean_amp[P1_mean_amp$emotion == 'angry',]$x - P1_mean_amp[P1_mean_amp$emotion == 'neutral',]$x
  
# N170 across hemispheres
  N170_mean_amp = aggregate(N170_stat$ROI_GA_amp,
            list(ID = N170_stat$ID,
            emotion = N170_stat$emotion), mean)

  qn_data$N170_amp_hap = N170_mean_amp[N170_mean_amp$emotion == 'happy',]$x
  qn_data$N170_amp_ang = N170_mean_amp[N170_mean_amp$emotion == 'angry',]$x
  qn_data$N170_amp_neu = N170_mean_amp[N170_mean_amp$emotion == 'neutral',]$x
  
  qn_data$N170_amp_hap_neu = N170_mean_amp[N170_mean_amp$emotion == 'happy',]$x - N170_mean_amp[N170_mean_amp$emotion == 'neutral',]$x
  qn_data$N170_amp_ang_neu = N170_mean_amp[N170_mean_amp$emotion == 'angry',]$x - N170_mean_amp[N170_mean_amp$emotion == 'neutral',]$x
  
# N170 left hemisphere
  N170_left_mean_amp = aggregate(N170_stat[N170_stat$hem == "left",]$ROI_GA_amp,
            list(ID = N170_stat[N170_stat$hem == "left",]$ID,
            emotion = N170_stat[N170_stat$hem == "left",]$emotion), mean)
  
  qn_data$N170_left_amp_hap = N170_left_mean_amp[N170_left_mean_amp$emotion == 'happy',]$x
  qn_data$N170_left_amp_ang = N170_left_mean_amp[N170_left_mean_amp$emotion == 'angry',]$x
  qn_data$N170_left_amp_neu = N170_left_mean_amp[N170_left_mean_amp$emotion == 'neutral',]$x
  
  qn_data$N170_left_amp_hap_neu = N170_left_mean_amp[N170_left_mean_amp$emotion == 'happy',]$x - N170_left_mean_amp[N170_left_mean_amp$emotion == 'neutral',]$x
  qn_data$N170_left_amp_ang_neu = N170_left_mean_amp[N170_left_mean_amp$emotion == 'angry',]$x - N170_left_mean_amp[N170_left_mean_amp$emotion == 'neutral',]$x
  
# N170 right hemisphere
  N170_right_mean_amp = aggregate(N170_stat[N170_stat$hem == "right",]$ROI_GA_amp,
            list(ID = N170_stat[N170_stat$hem == "right",]$ID,
            emotion = N170_stat[N170_stat$hem == "right",]$emotion), mean)
  
  qn_data$N170_right_amp_hap = N170_right_mean_amp[N170_right_mean_amp$emotion == 'happy',]$x
  qn_data$N170_right_amp_ang = N170_right_mean_amp[N170_right_mean_amp$emotion == 'angry',]$x
  qn_data$N170_right_amp_neu = N170_right_mean_amp[N170_right_mean_amp$emotion == 'neutral',]$x
  
  qn_data$N170_right_amp_hap_neu = N170_right_mean_amp[N170_right_mean_amp$emotion == 'happy',]$x - N170_right_mean_amp[N170_right_mean_amp$emotion == 'neutral',]$x
  qn_data$N170_right_amp_ang_neu = N170_right_mean_amp[N170_right_mean_amp$emotion == 'angry',]$x - N170_right_mean_amp[N170_right_mean_amp$emotion == 'neutral',]$x  
  
# P3
  P3_mean_amp = aggregate(P3_short_stat$ROI_GA_amp,
            list(ID = P3_short_stat$ID,
            emotion = P3_short_stat$emotion), mean)
  
  qn_data$P3_amp_hap = P3_mean_amp[P3_mean_amp$emotion == 'happy',]$x
  qn_data$P3_amp_ang = P3_mean_amp[P3_mean_amp$emotion == 'angry',]$x
  qn_data$P3_amp_neu = P3_mean_amp[P3_mean_amp$emotion == 'neutral',]$x

  qn_data$P3_amp_hap_neu = P3_mean_amp[P3_mean_amp$emotion == 'happy',]$x - P3_mean_amp[P3_mean_amp$emotion == 'neutral',]$x
  qn_data$P3_amp_ang_neu = P3_mean_amp[P3_mean_amp$emotion == 'angry',]$x - P3_mean_amp[P3_mean_amp$emotion == 'neutral',]$x  
  
# Calculate latency mean for each ERP component and difference scores between emotions 

# P1
  P1_mean_lat = aggregate(P1_stat$ROI_GA_lat,
            list(ID = P1_stat$ID,
            emotion = P1_stat$emotion), mean)

  qn_data$P1_lat_hap = P1_mean_lat[P1_mean_lat$emotion == 'happy',]$x
  qn_data$P1_lat_ang = P1_mean_lat[P1_mean_lat$emotion == 'angry',]$x
  qn_data$P1_lat_neu = P1_mean_lat[P1_mean_lat$emotion == 'neutral',]$x
  
  qn_data$P1_lat_hap_neu = P1_mean_lat[P1_mean_lat$emotion == 'happy',]$x - P1_mean_lat[P1_mean_lat$emotion == 'neutral',]$x
  qn_data$P1_lat_ang_neu = P1_mean_lat[P1_mean_lat$emotion == 'angry',]$x - P1_mean_lat[P1_mean_lat$emotion == 'neutral',]$x
  
# N170 across hemispheres
  N170_mean_lat = aggregate(N170_stat$ROI_GA_lat,
            list(ID = N170_stat$ID,
            emotion = N170_stat$emotion), mean)

  qn_data$N170_lat_hap = N170_mean_lat[N170_mean_lat$emotion == 'happy',]$x
  qn_data$N170_lat_ang = N170_mean_lat[N170_mean_lat$emotion == 'angry',]$x
  qn_data$N170_lat_neu = N170_mean_lat[N170_mean_lat$emotion == 'neutral',]$x
  
  qn_data$N170_lat_hap_neu = N170_mean_lat[N170_mean_lat$emotion == 'happy',]$x - N170_mean_lat[N170_mean_lat$emotion == 'neutral',]$x
  qn_data$N170_lat_ang_neu = N170_mean_lat[N170_mean_lat$emotion == 'angry',]$x - N170_mean_lat[N170_mean_lat$emotion == 'neutral',]$x
  
  
# N170 left hemisphere
  N170_left_mean_lat = aggregate(N170_stat[N170_stat$hem == "left",]$ROI_GA_lat,
            list(ID = N170_stat[N170_stat$hem == "left",]$ID,
            emotion = N170_stat[N170_stat$hem == "left",]$emotion), mean)
  
  qn_data$N170_left_lat_hap = N170_left_mean_lat[N170_left_mean_lat$emotion == 'happy',]$x
  qn_data$N170_left_lat_ang = N170_left_mean_lat[N170_left_mean_lat$emotion == 'angry',]$x
  qn_data$N170_left_lat_neu = N170_left_mean_lat[N170_left_mean_lat$emotion == 'neutral',]$x
  
  qn_data$N170_left_lat_hap_neu = N170_left_mean_lat[N170_left_mean_lat$emotion == 'happy',]$x - N170_left_mean_lat[N170_left_mean_lat$emotion == 'neutral',]$x
  qn_data$N170_left_lat_ang_neu = N170_left_mean_lat[N170_left_mean_lat$emotion == 'angry',]$x - N170_left_mean_lat[N170_left_mean_lat$emotion == 'neutral',]$x
  
  
# N170 right hemisphere
  N170_right_mean_lat = aggregate(N170_stat[N170_stat$hem == "right",]$ROI_GA_lat,
            list(ID = N170_stat[N170_stat$hem == "right",]$ID,
            emotion = N170_stat[N170_stat$hem == "right",]$emotion), mean)
  
  qn_data$N170_right_lat_hap = N170_right_mean_lat[N170_right_mean_lat$emotion == 'happy',]$x
  qn_data$N170_right_lat_ang = N170_right_mean_lat[N170_right_mean_lat$emotion == 'angry',]$x
  qn_data$N170_right_lat_neu = N170_right_mean_lat[N170_right_mean_lat$emotion == 'neutral',]$x
  
  qn_data$N170_right_lat_hap_neu = N170_right_mean_lat[N170_right_mean_lat$emotion == 'happy',]$x - N170_right_mean_lat[N170_right_mean_lat$emotion == 'neutral',]$x
  qn_data$N170_right_lat_ang_neu = N170_right_mean_lat[N170_right_mean_lat$emotion == 'angry',]$x - N170_right_mean_lat[N170_right_mean_lat$emotion == 'neutral',]$x
    

# Count how many trials per participant / per emotion condition are left (take P1, all components have same number of artifact trials)
  trial_count = P1_stat %>% count(ID, emotion)
  
  qn_data$hap_trials = trial_count[trial_count$emotion == 'happy',]$n
  qn_data$ang_trials = trial_count[trial_count$emotion == 'angry',]$n
  qn_data$neu_trials = trial_count[trial_count$emotion == 'neutral',]$n
  
  
# Z-scoring for further analyses
  qn_data$z_P1_amp_ang = scale(qn_data$P1_amp_ang)
  qn_data$z_P1_amp_neu = scale(qn_data$P1_amp_neu)
  qn_data$z_P1_amp_hap = scale(qn_data$P1_amp_hap)
  qn_data$z_P1_amp_hap_neu = scale(qn_data$P1_amp_hap_neu)
  qn_data$z_P1_amp_ang_neu = scale(qn_data$P1_amp_ang_neu)
  qn_data$z_P1_lat_ang = scale(qn_data$P1_lat_ang)
  qn_data$z_P1_lat_neu = scale(qn_data$P1_lat_neu)
  qn_data$z_P1_lat_hap = scale(qn_data$P1_lat_hap)
  qn_data$z_P1_lat_hap_neu = scale(qn_data$P1_lat_hap_neu)
  qn_data$z_P1_lat_ang_neu = scale(qn_data$P1_lat_ang_neu)
  
  qn_data$z_N170_amp_ang = scale(qn_data$N170_amp_ang)
  qn_data$z_N170_amp_neu = scale(qn_data$N170_amp_neu)
  qn_data$z_N170_amp_hap = scale(qn_data$N170_amp_hap)
  qn_data$z_N170_amp_hap_neu = scale(qn_data$N170_amp_hap_neu)
  qn_data$z_N170_amp_ang_neu = scale(qn_data$N170_amp_ang_neu)
  qn_data$z_N170_lat_ang = scale(qn_data$N170_lat_ang)
  qn_data$z_N170_lat_neu = scale(qn_data$N170_lat_neu)
  qn_data$z_N170_lat_hap = scale(qn_data$N170_lat_hap)
  qn_data$z_N170_lat_hap_neu = scale(qn_data$N170_lat_hap_neu)
  qn_data$z_N170_lat_ang_neu = scale(qn_data$N170_lat_ang_neu)
  
  qn_data$z_N170_left_amp_ang = scale(qn_data$N170_left_amp_ang)
  qn_data$z_N170_left_amp_neu = scale(qn_data$N170_left_amp_neu)
  qn_data$z_N170_left_amp_hap = scale(qn_data$N170_left_amp_hap)
  qn_data$z_N170_left_amp_hap_neu = scale(qn_data$N170_left_amp_hap_neu)
  qn_data$z_N170_left_amp_ang_neu = scale(qn_data$N170_left_amp_ang_neu)
  qn_data$z_N170_left_lat_ang = scale(qn_data$N170_left_lat_ang)
  qn_data$z_N170_left_lat_neu = scale(qn_data$N170_left_lat_neu)
  qn_data$z_N170_left_lat_hap = scale(qn_data$N170_left_lat_hap)
  qn_data$z_N170_left_lat_hap_neu = scale(qn_data$N170_left_lat_hap_neu)
  qn_data$z_N170_left_lat_ang_neu = scale(qn_data$N170_left_lat_ang_neu)
  
  qn_data$z_N170_right_amp_ang = scale(qn_data$N170_right_amp_ang)
  qn_data$z_N170_right_amp_neu = scale(qn_data$N170_right_amp_neu)
  qn_data$z_N170_right_amp_hap = scale(qn_data$N170_right_amp_hap)
  qn_data$z_N170_right_amp_hap_neu = scale(qn_data$N170_right_amp_hap_neu)
  qn_data$z_N170_right_amp_ang_neu = scale(qn_data$N170_right_amp_ang_neu)
  qn_data$z_N170_right_lat_ang = scale(qn_data$N170_right_lat_ang)
  qn_data$z_N170_right_lat_neu = scale(qn_data$N170_right_lat_neu)
  qn_data$z_N170_right_lat_hap = scale(qn_data$N170_right_lat_hap)
  qn_data$z_N170_right_lat_hap_neu = scale(qn_data$N170_right_lat_hap_neu)
  qn_data$z_N170_right_lat_ang_neu = scale(qn_data$N170_right_lat_ang_neu)
  
  qn_data$z_P3_amp_ang = scale(qn_data$P3_amp_ang)
  qn_data$z_P3_amp_neu = scale(qn_data$P3_amp_neu)
  qn_data$z_P3_amp_hap = scale(qn_data$P3_amp_hap)
  qn_data$z_P3_amp_hap_neu = scale(qn_data$P3_amp_hap_neu)
  qn_data$z_P3_amp_ang_neu = scale(qn_data$P3_amp_ang_neu)
  
# Mean-centering for further analyses
  qn_data$mc_P1_amp_ang = scale(qn_data$P1_amp_ang, scale = F)
  qn_data$mc_P1_amp_neu = scale(qn_data$P1_amp_neu, scale = F)
  qn_data$mc_P1_amp_hap = scale(qn_data$P1_amp_hap, scale = F)
  qn_data$mc_P1_amp_hap_neu = scale(qn_data$P1_amp_hap_neu, scale = F)
  qn_data$mc_P1_amp_ang_neu = scale(qn_data$P1_amp_ang_neu, scale = F)
  qn_data$mc_P1_lat_ang = scale(qn_data$P1_lat_ang, scale = F)
  qn_data$mc_P1_lat_neu = scale(qn_data$P1_lat_neu, scale = F)
  qn_data$mc_P1_lat_hap = scale(qn_data$P1_lat_hap, scale = F)
  qn_data$mc_P1_lat_hap_neu = scale(qn_data$P1_lat_hap_neu, scale = F)
  qn_data$mc_P1_lat_ang_neu = scale(qn_data$P1_lat_ang_neu, scale = F)
  
  qn_data$mc_N170_amp_ang = scale(qn_data$N170_amp_ang, scale = F)
  qn_data$mc_N170_amp_neu = scale(qn_data$N170_amp_neu, scale = F)
  qn_data$mc_N170_amp_hap = scale(qn_data$N170_amp_hap, scale = F)
  qn_data$mc_N170_amp_hap_neu = scale(qn_data$N170_amp_hap_neu, scale = F)
  qn_data$mc_N170_amp_ang_neu = scale(qn_data$N170_amp_ang_neu, scale = F)
  qn_data$mc_N170_lat_ang = scale(qn_data$N170_lat_ang, scale = F)
  qn_data$mc_N170_lat_neu = scale(qn_data$N170_lat_neu, scale = F)
  qn_data$mc_N170_lat_hap = scale(qn_data$N170_lat_hap, scale = F)
  qn_data$mc_N170_lat_hap_neu = scale(qn_data$N170_lat_hap_neu, scale = F)
  qn_data$mc_N170_lat_ang_neu = scale(qn_data$N170_lat_ang_neu, scale = F)
  
  qn_data$mc_N170_left_amp_ang = scale(qn_data$N170_left_amp_ang, scale = F)
  qn_data$mc_N170_left_amp_neu = scale(qn_data$N170_left_amp_neu, scale = F)
  qn_data$mc_N170_left_amp_hap = scale(qn_data$N170_left_amp_hap, scale = F)
  qn_data$mc_N170_left_amp_hap_neu = scale(qn_data$N170_left_amp_hap_neu, scale = F)
  qn_data$mc_N170_left_amp_ang_neu = scale(qn_data$N170_left_amp_ang_neu, scale = F)
  qn_data$mc_N170_left_lat_ang = scale(qn_data$N170_left_lat_ang, scale = F)
  qn_data$mc_N170_left_lat_neu = scale(qn_data$N170_left_lat_neu, scale = F)
  qn_data$mc_N170_left_lat_hap = scale(qn_data$N170_left_lat_hap, scale = F)
  qn_data$mc_N170_left_lat_hap_neu = scale(qn_data$N170_left_lat_hap_neu, scale = F)
  qn_data$mc_N170_left_lat_ang_neu = scale(qn_data$N170_left_lat_ang_neu, scale = F)
  
  qn_data$mc_N170_right_amp_ang = scale(qn_data$N170_right_amp_ang, scale = F)
  qn_data$mc_N170_right_amp_neu = scale(qn_data$N170_right_amp_neu, scale = F)
  qn_data$mc_N170_right_amp_hap = scale(qn_data$N170_right_amp_hap, scale = F)
  qn_data$mc_N170_right_amp_hap_neu = scale(qn_data$N170_right_amp_hap_neu, scale = F)
  qn_data$mc_N170_right_amp_ang_neu = scale(qn_data$N170_right_amp_ang_neu, scale = F)
  qn_data$mc_N170_right_lat_ang = scale(qn_data$N170_right_lat_ang, scale = F)
  qn_data$mc_N170_right_lat_neu = scale(qn_data$N170_right_lat_neu, scale = F)
  qn_data$mc_N170_right_lat_hap = scale(qn_data$N170_right_lat_hap, scale = F)
  qn_data$mc_N170_right_lat_hap_neu = scale(qn_data$N170_right_lat_hap_neu, scale = F)
  qn_data$mc_N170_right_lat_ang_neu = scale(qn_data$N170_right_lat_ang_neu, scale = F)
  
  qn_data$mc_P3_amp_ang = scale(qn_data$P3_amp_ang, scale = F)
  qn_data$mc_P3_amp_neu = scale(qn_data$P3_amp_neu, scale = F)
  qn_data$mc_P3_amp_hap = scale(qn_data$P3_amp_hap, scale = F)
  qn_data$mc_P3_amp_hap_neu = scale(qn_data$P3_amp_hap_neu, scale = F)
  qn_data$mc_P3_amp_ang_neu = scale(qn_data$P3_amp_ang_neu, scale = F)  

  
# Save in Rdata format
  save(qn_data, file = "./data/qn_data.RData")

```
