---
title: "Introduction"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center")
  knitr::opts_knit$set(width=75)
  
# Set libraries
  library(kableExtra)
  library(tidyverse)
  library(XLConnect)

# Swipe environment
  rm(list=ls())
  
```

# Study description

The development of socio-emotional competencies (SEC) has proven key for school and life success as well as for preventing mental illness. Digital SEC trainings create new ways to strengthen children’s mental health especially in times of disrupted childcare and subsequent increase of mental health problems due to the COVID-19 pandemic. Despite the potential benefits, few studies examined the effectiveness of digital SEC trainings in young children. In a six-week study, we tested the digital SEC training Zirkus Empathico with four- to six-year-old typically developing children (N = 60) using parent and child SEC ratings as well as EEG. The registered primary outcome was empathy (GEM, EMK 3-6); secondary outcomes included emotion knowledge (EMK 3-6), prosocial behavior (SDQ), reduction of problematic behaviors (SDQ), and children’s neural sensitivity to facial expressions quantified with early (P1, N170) and late (P3) event-related potentials. Compared to age- and gender-matched controls (N = 30), the Zirkus Empathico group (N = 30) showed increases in empathy, emotion recognition, prosocial behavior and reduced behavioral problems post-training and increases in empathy in a three months follow-up. Zirkus Empathico participants had larger P3 amplitudes for happy vs. neutral facial expressions, whereas larger P3 amplitudes for angry vs. neutral facial expressions were found for control participants.Given the training group’s improvements across behavioral measures, Zirkus Empathico may be a promising digital SEC training. EEG results seem to corroborate behavioral findings: The training group allocated more neural resources toward happy faces potentially indicative of training-induced, accelerated maturation regarding the regulation of positive emotional states. 

Pre-regristration of the project can be found [here](https://drks.de/drks_web/navigate.do?navigationId=trial.HTML&TRIAL_ID=DRKS00015789).

# Overview of data sets 

To reproduce our analysis, you need the following datasets: 

```{r overview, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx", 
                               sheet = "all_data", 
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)
```

