---
title: "Introduction"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center")
  knitr::opts_knit$set(width=75)
  
# Set libraries
  library(kableExtra)
  library(tidyverse)
  library(XLConnect)

# Swipe environment
  rm(list=ls())
  
```

# Study description

In this randomized controlled trial the digital socio-emotional competence training Zirkus Empathico was tested in 74 Central European children (5.1(0.9) years; 34 females). The preregistered primary outcome was empathy, secondary outcomes included emotion recognition, prosocial behavior, behavioral problem reduction, and children’s neural sensitivity to facial expressions quantified with event-related potentials. Compared to controls, Zirkus Empathico participants showed increases in empathy (d = 0.28 [-0.17, 0.76]), emotion recognition (d = 0.57 [0.01, 1.06]), prosocial behavior (d = 0.51 [0.05, 0.99]) and reduced behavioral problems (d = 0.54 [0.08, 1.03]). They also showed larger P3 amplitudes to happy vs. angry and neutral facial expressions post training. Thus, Zirkus Empathico may be a promising digital training for social competence in preschoolers. 

Pre-registration of the project can be found [here](https://drks.de/drks_web/navigate.do?navigationId=trial.HTML&TRIAL_ID=DRKS00015789).

# Overview of data sets 

To reproduce our analysis, you need the following datasets: 

```{r overview, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx", 
                               sheet = "all_data", 
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)
```

